Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-06-10 paper/galsize_paper.tex
Updated notebook and plots to include jackknife error estimation for clustering ratios

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/rvir_only_wp_ratios.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass. Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
}
\label{fig:clustering_ratio_upshot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios, denoted as $\delta\wproj/\wproj,$ are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. As a specific example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.

@@

Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}). Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides. In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.  This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable. The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/rvir_only_wp_ratios.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass. Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, with gray bands showing our jackknife error estimation. Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
}
\label{fig:clustering_ratio_upshot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios, denoted as $\delta\wproj/\wproj,$ are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. As a specific example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass. The gray bands enveloping each curve show our $1\sigma$ error bars, estimated by jackknifing 125 subvolumes.

@@

Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}). Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides. In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.  This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable. The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies. Error bars are not shown for this model but they are comparable to the errors shown on the purple curves calculated through same jackknife estimation method used in Figure~\ref{fig:clustering_ratio_upshot}.
